<script type="text/x-mathjax-config">
  MathJax.Hub.Config({
    displayAlign: "left",
    "HTML-CSS": { scale: 175 }
  });
</script>

Results of run "[2x2x2]"
========================================================

# 1\. Data procesing and analyses

## 1\.1 Batch results pre-processing (probably you can skip this)

Reading the summary result data which describes a state when simulation finds the equilibrium.

Let me just point the directory.

```{r, message=F, warning=F}
wd <- "/mnt/data1/oskar/symulacje-github/simphony_model_1429396999980/"
library(dplyr)
library(sqldf)
```

And load the data.

```{r}
batch_1 <- read.csv(paste(wd,'instance_1/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_2 <- read.csv(paste(wd,'instance_2/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_3 <- read.csv(paste(wd,'instance_3/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_4 <- read.csv(paste(wd,'instance_4/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_5 <- read.csv(paste(wd,'instance_5/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_6 <- read.csv(paste(wd,'instance_6/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_7 <- read.csv(paste(wd,'instance_7/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_8 <- read.csv(paste(wd,'instance_8/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_9 <- read.csv(paste(wd,'instance_9/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
batch_10 <- read.csv(paste(wd,'instance_10/batch.log',sep=""), sep=",", quote="", header = TRUE, dec=".")
```

What the single's file size?

```{r}
typeof(batch_1)
length(batch_1)
```

Number of all results (hence the merge)

```{r}
nrow(batch_1) + nrow(batch_2) + nrow(batch_3) + nrow(batch_4) + nrow(batch_5) +
  nrow(batch_6) + nrow(batch_7) + nrow(batch_8) + 
  nrow(batch_9) + nrow(batch_10)
```

Merging results into one dataframe

```{r}
batch_merged <- sqldf("select * from batch_1 union select * from batch_2 union select * from batch_3 union select * from batch_4  
                      union select * from batch_5 union select * from batch_6 union select * from batch_7 union select * from batch_8 
                      union select * from batch_9 union select * from batch_10")

batch_merged$Experience_Decay <- as.logical(batch_merged$Experience_Decay=='true')
batch_merged$Allow_Skill_Death <- as.logical(batch_merged$Allow_Skill_Death=='true')
batch_merged$Fll_Enabled <- as.logical(batch_merged$Fll_Enabled=='true')
batch_merged$Exp_cut_point <- as.logical(batch_merged$Exp_cut_point=='true')
batch_merged$Granularity <- as.logical(batch_merged$Granularity=='true')
batch_merged$Is_Evolutionary <- as.logical(batch_merged$Is_Evolutionary=='true')
batch_merged$Allways_Choose_Task <- as.logical(batch_merged$Allways_Choose_Task=='true')
```

Setting indexes

```{r}
result_idx1 <- sqldf("create index idx_batch_run on batch_merged(Run_Number)")
```
```{r}
typeof(batch_merged)
sapply(batch_merged, class)
```

Show head and tail of merged batch results

```{r}
# head(batch_merged)  -- to long output, skip
# tail(batch_merged)  -- to long output, skip
```

Generate vector of combinations

```{r}
combination_of_param <- expand.grid(
  c(TRUE, FALSE), 
  c(50, 120),
  c(20, 100))
typeof(combination_of_param)
combination_of_param
my_col_names <- c(
  'ExpDecay',
  'AgentCount', 
  'GenerationLength')
colnames(combination_of_param) <- my_col_names
typeof(combination_of_param)
```

We have set of 8 options [2 x 2 x 2]

```{r}
covering <- sqldf("select Experience_Decay, Agents_Count, GenerationLength, 
                  count(*) as occurences, 
                  'ExpDec-' || Experience_Decay || '-A-' || Agents_Count || '-GL-' || GenerationLength as optgrp
                  from batch_merged group by Experience_Decay, Agents_Count, GenerationLength")
min(covering$occurences)
max(covering$occurences)
sd(covering$occurences)
```

```{r}
# head(covering) -- to long output, skip
# sqldf("update batch_merged b set b.opt = (select distinct p.optgrp from covering p where p.Experience_Decay = b.Experience_Decay and p.Agents_Count = b.Agents_Count and p.GenerationLength = b.GenerationLength)")
batch_merged <- sqldf("select b.*, p.optgrp as OptionGroup, '' as winning from batch_merged b join covering p on (p.Experience_Decay = b.Experience_Decay and p.Agents_Count = b.Agents_Count and p.GenerationLength = b.GenerationLength)")
# head(batch_merged,5) -- to long output, skip
# tail(batch_merged) -- to long output, skip
nrow(batch_merged)
```

## 1\.2 Ploting time of simulation closure

Box plots of time execution

```{r, fig.width = 15}
library(ggplot2) 
# Boxplots of task count by scenario number
# observations (points) are overlayed and jittered
qplot(OptionGroup, Tick_Count, data=batch_merged, geom=c("boxplot", "jitter"),
   fill=OptionGroup, main="Tick count per different scenario",
   xlab="", ylab="Number of ticks") + stat_boxplot(geom ='errorbar')
```

## 1\.3 Ploting winning strategies

```{r}
batch_merged <- sqldf(c("update batch_merged set winning = 'mix' where (Homophily_Count BETWEEN 1 AND Agents_Count - 1) or (Heterophily_Count BETWEEN 1 AND Agents_Count - 1) or (Preferential_Count BETWEEN 1 AND Agents_Count - 1)", "select * from batch_merged"))
batch_merged <- sqldf(c("update batch_merged set winning = 'hom' where Homophily_Count = Agents_Count", "select * from batch_merged"))
batch_merged <- sqldf(c("update batch_merged set winning = 'het' where Heterophily_Count = Agents_Count", "select * from batch_merged"))
batch_merged <- sqldf(c("update batch_merged set winning = 'pre' where Preferential_Count = Agents_Count", "select * from batch_merged"))
winning <- sqldf("select OptionGroup as subscenario, sum(CASE WHEN winning='hom' THEN 1 ELSE 0 END) as homophily, sum(CASE WHEN winning='het' THEN 1 ELSE 0 END) as heterophily, sum(CASE WHEN winning='pre' THEN 1 ELSE 0 END) as preferential, sum(CASE WHEN winning='mix' THEN 1 ELSE 0 END) as mixed from batch_merged group by subscenario")
```

Table with winning strategies is produced here:

```{r table1, comment=NA, results='asis'}
library(xtable)
print(xtable(head(winning)), type = "html", include.rownames = F)
```

# 2\. Definitions

# 2\.1 Basic terms

* Experience

This have values between *0* and *1* returned by a sigmoid function.

```{r}
sigmoid <- function(x) {
  1 / ( 1 + exp(-x) )
}
point <- 0.75 * 12 - 6
qplot(c(-6, 6), stat="function", fun=sigmoid, geom="line") + geom_point(aes(point), y=sigmoid(point), colour="red")
```

And, for example, if agent worked 3000 units on Java which mastering requires 4000 units, he have experience equal sigmoid(0.75 * 12 - 6) because 3000/4000 = 0.75

# 2\.2 Algorithms descriptions

* Similarity

$$
Similarity_{MIN} = 
\begin{pmatrix}
0 & \iff A \cap T = \varnothing \\

\begin{smallmatrix}
  min \\
  s \in A \cap T
\end{smallmatrix}

(\xi_s^A) & \iff A \cap T \neq \varnothing
\end{pmatrix}
$$

$$
Similarity_{MAX} = 
\begin{pmatrix}
0 & \iff A \cap T = \varnothing \\

\begin{smallmatrix}
  max \\
  s \in A \cap T
\end{smallmatrix}

(\xi_s^A) & \iff A \cap T \neq \varnothing
\end{pmatrix}
$$

* Homophily

This strategy searches for $argmax(Similarity_{MAX}(A,T))$

* Heterophily

This strategy searches for $argmin(Similarity_{MIN}(A,T))$

* Preferential

Get all tasks with having at least one agent skill and chose task with highest number of *visits*. In a situation in which tasks having user skills where never 'worked on' (*visited*) yet, chose a *most done* task. Also chose a *most done* task when there are no tasks matching user skill.

# 3\. Agents state and their learning process

* Utility function

Learning function is a sum of two parts, left part is *the lowest single experience* from set of Agent's skills, right part is a *sum of Agent's experiences* multiplied by factor *0.05*.

$$latex
min \xi _i + \varepsilon \cdot \sum_{i}^{n} \xi_i
$$
